Efficient Compilation of High Level Python Numerical Programs with Pythran

### 2014-09-03 doc/papers/cgo2014/paper.tex
Add raw results

>>>>

\begin{table*}

    \centering{
\begin{tabular}{|l||c|c|c|c|c|}
\hline
& Python & numba & parakeet & pypy & pythran \\
\hline
\hline
       allpairs\_distances &   37727 &             0 &          1768 &         36855 & \textbf{1079} \\
allpairs\_distances\_loops &   49799 &         55867 &          1781 &         50253 & \textbf{1758} \\
             arc\_distance &    1365 &          1401 &          1596 &          1364 &  \textbf{494} \\
                      conv & 1926454 &       2356675 &          2032 &       1899006 & \textbf{1944} \\
              create\_grid &    3867 &          3950 &             0 & \textbf{3833} &          5512 \\
                  cronbach &    1637 &          1681 &             0 &          1756 & \textbf{1136} \\
                 diffusion &   22511 &         23564 &         21167 &         22450 & \textbf{9606} \\
                    evolve &    5762 &             0 &             0 &          5522 & \textbf{3841} \\
                      fdtd & 1558799 &       1824395 &             0 &       1538692 & \textbf{1198} \\
                       fft &   25720 &             0 &             0 &         24771 & \textbf{1211} \\
                  grouping &    2095 &             0 &             0 &          2104 &  \textbf{839} \\
                   growcut & 1807849 &          5573 & \textbf{2200} &       1860926 &          3930 \\
                    harris &    5516 &          5258 &          5084 &          5500 & \textbf{2994} \\
                   hyantes &  259268 &             0 & \textbf{1865} &        261074 &          2359 \\
                     julia & 2716770 &          2716 &          2930 &       2776183 & \textbf{2636} \\
                    l2norm &    6057 &          6008 &         12574 &          6069 &  \textbf{540} \\
             local\_maxima &   59822 &             0 &             0 &         60504 & \textbf{5084} \\
                    lstsqr &    7886 &          8652 &             0 &          7891 & \textbf{1680} \\
                    mandel &  437908 & \textbf{4361} &             0 &        439827 &          5075 \\
             multiple\_sum &    2981 &          3194 &          8206 &          2975 & \textbf{2007} \\
                  pairwise & 3888235 &          5777 &          3699 &       3873927 & \textbf{3435} \\
            periodic\_dist &    1848 &          1983 &             0 &          1863 &  \textbf{951} \\
                 repeating &    1216 &          1228 &             0 &          1226 &  \textbf{568} \\
           reverse\_cumsum &    2620 &          2629 &             0 &          2614 & \textbf{2389} \\
                     rosen &   14693 &         19419 &          1557 &         14611 &  \textbf{894} \\
                 slowparts &    5687 &             0 & \textbf{1223} &          5900 &          1537 \\
                 smoothing &  911126 & \textbf{4858} &          6258 &        935202 &          4924 \\
           specialconvolve &    8211 &          6665 &         10340 &          8140 & \textbf{2449} \\
              vibr\_energy &    2563 &          2450 &          2488 &          2548 & \textbf{1112} \\
                      wave &   54234 &         54529 &             0 &         51471 & \textbf{1886} \\
                     wdist &   82669 &         90274 & \textbf{1457} &         80406 &          1469 \\
\hline
\end{tabular}
}
\caption{Average execution times for all kernels of the numpy-benchamrks.}
\end{table*}
